My title

### 2024-03-12 paper/paper.qmd
Edits

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "My title"
author: "Bernice(Yixuan) Bao, Zheng(Zeb) Yang, Dongli Sun"
thanks: "Code and data are available at: LINK."
date: "March 11, 2024"
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---
